|

### 2020-12-07 appendix/appendix.Rmd
small edits to appendix and readme

Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the log of expenduture per capita. To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.

@@

Therefore, we see that majoritarian systems do not have a clear positive effect on budgetary spending. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are non-significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.

@@

## Meta-Regressions for the Log of Expenditure Per Capita

@@

Gor the meta-regressions of Log of Expenditure Per Capita we find no significant results.

>>>>

Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the log of expenditure per capita. To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.

@@

Therefore, we see that majoritarian systems do not have a clear positive effect on budgetary spending. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are not statistically significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.

@@

## Meta-Regressions for Log of Expenditure Per Capita

@@

For the meta-regressions of Log of Expenditure Per Capita we find no significant results.
